### 2017-12-27 icde/revision/sec-exp.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Accuracy evaluation with \recom}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
\hline \hline
\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-4ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\newcommand{\graphscale}{0.36} %0.38
\newcommand{\graphmargin}{-4ex}
\newcommand{\exppath}{./exp/}
%\newcommand{\exppath}{./exp/wpr/}
%%% all in 1 Figure
\begin{figure*}[tb!]
%\vspace{-2ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-futureyear}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-t}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-sigma}
\includegraphics[scale=\graphscale]{./exp/AAN_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-lambda}
\includegraphics[scale=\graphscale]{./exp/AAN_lambda.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-futureyear}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-t}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-sigma}
\includegraphics[scale=\graphscale]{./exp/AMiner_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-lambda}
\includegraphics[scale=\graphscale]{./exp/AMiner_lambda.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-futureyear}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-t}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-fcdiff}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-sigma}
\includegraphics[scale=\graphscale]{./exp/MAG_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-lambda}
\includegraphics[scale=\graphscale]{./exp/MAG_lambda.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Accuracy evaluation with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
\label{exp-pairacc}
\vspace{-1ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-aminer-time1}
\includegraphics[scale=\graphscale]{./exp/AMiner_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-aminer-time2}
\includegraphics[scale=\graphscale]{./exp/AMiner_time.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-mag-time1}
\includegraphics[scale=\graphscale]{./exp/MAG_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-mag-time2}
\includegraphics[scale=\graphscale]{./exp/MAG_time.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Efficiency evaluation on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
\label{exp-time}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

When varying $dif$, the \PairAcc of all algorithms increases with the increment of $dif$, since scholarly article pairs with larger $dif$ are easier to rank. Moreover, \ensemblerank consistently ranks better than all competitors, regardless of easy or difficult article pairs. Indeed, \ensemblerank improves the \PairAcc over (\pagerank, \futurerank, \hhgrank) by (12.0\%, 3.0\%, 3.2\%) on \aan, (14.0\%, 6.5\%, 4.6\%) on \aminer, and (13.4\%, 6.0\%, 2.4\%) on \magdata, on average, respectively.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.25}
\newcommand{\graphmarginexpapp}{-2ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Accuracy evaluation: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Accuracy evaluation using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
\label{tab-recom}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c| c |c | c|}
\hline
{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
\hline \hline
% \recom
\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
% \ficta
\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-4ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Impacts of TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights directly without introducing the peak time.
The \PairAcc difference of these two algorithms is higher with \recom than with \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.
Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.
%, which, with \recom and \fcita, improves the \PairAcc by (2.88\%, 3.91\%, 3.90\%) and (0.55\%, 0.50\%, 0.22\%) on (\aan, \aminer, \magdata) on average, respectively.
The improvement decreases with the decrease of $\lambda$ as the popularity dominates the ranking with small $\lambda$, and in some cases, \drank outperforms \ensemblerank. %as the prestige and popularity orders of article pairs are more diverse for \drank than \ensemblerank.
Overall, with \recom and \fcita, \ensemblerank improves the \PairAcc over \drank by (1.78\%, 3.07\%, 3.20\%) and (0.29\%, 0.48\%, 0.11\%) on (\aan, \aminer, \magdata) on average, respectively.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Accuracy evaluation with \recom}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
\hline \hline
\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\newcommand{\graphscale}{0.36} %0.38
\newcommand{\graphmargin}{-4ex}
\newcommand{\exppath}{./exp/}
%\newcommand{\exppath}{./exp/wpr/}
%%% all in 1 Figure
\begin{figure*}[tb!]
%\vspace{-2ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-futureyear}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-t}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-sigma}
\includegraphics[scale=\graphscale]{./exp/AAN_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-lambda}
\includegraphics[scale=\graphscale]{./exp/AAN_lambda.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-futureyear}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-t}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-sigma}
\includegraphics[scale=\graphscale]{./exp/AMiner_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-lambda}
\includegraphics[scale=\graphscale]{./exp/AMiner_lambda.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-futureyear}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-t}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-fcdiff}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-sigma}
\includegraphics[scale=\graphscale]{./exp/MAG_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-lambda}
\includegraphics[scale=\graphscale]{./exp/MAG_lambda.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Accuracy evaluation with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
\label{exp-pairacc}
\vspace{-1ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-aminer-time1}
\includegraphics[scale=\graphscale]{./exp/AMiner_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-aminer-time2}
\includegraphics[scale=\graphscale]{./exp/AMiner_time.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-mag-time1}
\includegraphics[scale=\graphscale]{./exp/MAG_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-mag-time2}
\includegraphics[scale=\graphscale]{./exp/MAG_time.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Efficiency evaluation on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
\label{exp-time}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

When varying $dif$, the \PairAcc of all algorithms increases with the increment of $dif$, since pairs with larger $dif$ are easier to rank. Moreover, \ensemblerank consistently ranks better, regardless of easy or difficult article pairs. Indeed, \ensemblerank improves the \PairAcc over (\pagerank, \futurerank, \hhgrank) by (12.0\%, 3.0\%, 3.2\%) on \aan, (14.0\%, 6.5\%, 4.6\%) on \aminer, and (13.4\%, 6.0\%, 2.4\%) on \magdata, on average, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.24}
\newcommand{\graphmarginexpapp}{3ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Accuracy evaluation: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Accuracy evaluation using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
\label{tab-recom}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c| c |c | c|}
\hline
{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
\hline \hline
% \recom
\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
% \ficta
\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Impacts of TWPageRank on accuracy: varying importance weighting factor $\lambda$}
\label{exp-drank}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than directly decaying without introducing the peak time.
The \PairAcc difference of these two algorithms is higher with \recom than with \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.
Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.
%, which, with \recom and \fcita, improves the \PairAcc by (2.88\%, 3.91\%, 3.90\%) and (0.55\%, 0.50\%, 0.22\%) on (\aan, \aminer, \magdata) on average, respectively.
The improvement decreases with the decrease of $\lambda$ as the popularity dominates the ranking with small $\lambda$, and in some cases, \drank outperforms \ensemblerank. %as the prestige and popularity orders of article pairs are more diverse for \drank than \ensemblerank.
Overall, with \recom and \fcita, \ensemblerank improves the \PairAcc over \drank by (1.78\%, 3.07\%, 3.20\%) and (0.29\%, 0.48\%, 0.11\%) on (\aan, \aminer, \magdata) on average, respectively.
